### 2022-12-23 paper.Rmd
updates

meanRMSE <- rowMeans(sima)
names(meanRMSE) <- n
round(meanRMSE, 2)
matplot(nvec, log(sima), type = "l", col = 1, lty = 1,
ylab = "log(RMSE)", xlab = "sample size",
main = "Graded Response Model", xaxt = "n")
axis(1, at = nvec)
```

@@

#item 26 representative OCC
item26.icc <- ggicc(observe.fit.2,6,6)+ggtitle("Representative OCC: item26")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

@@

problematic_icc <- cowplot::plot_grid(item26.icc,item03.icc,item17.icc,
  item22.icc,item38.icc,item39.icc,
                               labels = "AUTO",
                               align="v",
                               ncol = 3,
                               label_size = 12,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

@@

personfit <- cowplot::plot_grid(observe.per.fit, des.per.fit, act.per.fit, nonj.per.fit, nonr.per.fit, labels = "AUTO",ncol=3, label_size = 12,align = "v",
                  label_fontface = "plain")

@@

TIC.plot <- cowplot::plot_grid(observe.TIC.1,describe.TIC.1, awareness.TIC.1,
                                   nonjudge.TIC.1,nonreact.TIC.1,
                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 90,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/PNG/Fig6.png",TIC.plot, units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

```{r Regression, eval=FALSE, include=FALSE}
library(lessR)

EI.regression <- lessR::Regression(EI ~ Observe + Describe +	Awareness  +	Nonjudge +	Nonreact, data =validity.cor )
Depression.regression <- lessR::Regression(EI ~ Depression + Describe +	Awareness  +	Nonjudge +	Nonreact, data =validity.cor )
MASS.regression <- lessR::Regression(MASS ~ Depression + Describe +	Awareness  +	Nonjudge +	Nonreact, data =validity.cor)
Openness.regression <- lessR::Regression(Openness ~ Depression + Describe +	Awareness  +	Nonjudge +	Nonreact, data =validity.cor )
Extraversion.regression <- lessR::Regression(Extraversion ~ Depression + Describe +	Awareness  +	Nonjudge +	Nonreact, data =validity.cor )
Neurotic.regression <- lessR::Regression(Neurotic ~ Depression + Describe +	Awareness  +	Nonjudge +	Nonreact, data =validity.cor )

>>>>

meanRMSE <- rowMeans(sima)
names(meanRMSE) <- n
round(meanRMSE, 2) #1.34-1.36
matplot(nvec, log(sima), type = "l", col = 1, lty = 1,
ylab = "log(RMSE)", xlab = "sample size",
main = "Graded Response Model", xaxt = "n")
axis(1, at = nvec)
```

@@

#item 26 representative OCC
item26.icc <- ggicc(observe.fit.2,6,6)+ggtitle("item26")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

@@

problematic_icc <- cowplot::plot_grid(item26.icc,item03.icc,item17.icc,
  item22.icc,item38.icc,item39.icc,
                               labels = "auto",
                               align="v",
                               ncol = 3,
                               label_size = 80,
                               label_fontfamily = "sans",
                               label_fontface = "plain")

@@

personfit <- cowplot::plot_grid(observe.per.fit, des.per.fit, act.per.fit, nonj.per.fit, nonr.per.fit, labels = "auto",ncol=3, label_size = 80,align = "v",
                  label_fontface = "plain")

@@

TIC.plot <- cowplot::plot_grid(observe.TIC.1,describe.TIC.1, awareness.TIC.1,
                                   nonjudge.TIC.1,nonreact.TIC.1,
                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 80,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/PNG/Fig6.png",TIC.plot, units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@
